\chapter{Suggestions to Improve the Existing System}

\section{System Perspective}

\section{External Interfaces}

\section{Functions}

\section{Usability Requirements}
\begin{itemize}
    \item The mobile app should run on Android version 7.0+ since about 5 percent of android devices are still running on this version.
    \item The mobile app should run on IOS 15+ since 96\% of IOS users are using IOS 15 and 16.
    \item The mobile app should support PDF view for users to be able to see the PDF they Downloaded without any issues.
    \item Mobile app shall support accessibility modes on Android and IOS for users with disablities.
    \item Mobile app shall work in sync with AI assistants; Google Assistant, Siri and Bixby.
    \item Size of the app must be less than 10 megabytes, so that users can download it less than a minute.
\end{itemize}
\section{Performance Requirements}
\begin{itemize}
    \item Mobile app should start in 2 seconds after click, on a mid-level Android and old IOS device.
    \item Mobile app should cache datas to be able to show them during connection unstablities.
\end{itemize}
\section{Logical Database Requirements}
\begin{itemize}
    \item A local database should be created for mobile app to cache data.
    \item This database should contain all data available for a selected city.
\end{itemize}
\section{Design Constraints}
\begin{itemize}
    \item Mobile app should be designed in a way that it should not store, collect or send any inappropriate information about user.
    \item While app is being deleted, all data should be deleted to prevent data leak of users.
\end{itemize}
\section{System Attributes}
\subsection{Reliablity}
\begin{itemize}
    \item Fails on mobile application should be less than 5 seconds in 10 minutes of use.
    \item The app should crash at most once in 20 uses.
\end{itemize}

\subsection{Availability}
\begin{itemize}
    \item Users should be able to use old versions of app after updates for 30 days.
    \item App should be available for all 3 major operating systems; IpadOS, IOS, Android.
\end{itemize}

\subsection{Security}
\begin{itemize}
    \item App should be running in sandbox mode, ie. It should not reach any data on users device.
\end{itemize}

\section{Supporting Information}
All the APIs of afetbilgi.com, and the mobile app Afetbilgi, will be open source and free forever.