\chapter{Introduction}

\section{Purpose and Objectives of afetbilgi.com}

Afetbilgi.com is a website that tries to deliver accurate information to people.
After the Pazarcik Earthquake, there was a lot of misinformation on social media platforms, and the infrastructure quality in the earthquake zone was terrible. 
Therefore people who needed help were having trouble finding the correct information.
Thanks to afetbilgi.com, it delivers the correct information with accuracy, speed, and simplicity principles.

\section{Scope}

The website is named afetbilgi.com, and the users will be able to reach important telephone numbers and locations in a disaster situation. \\
The scope of the system can be listed as \\
\begin{itemize}
    \item The system provides users with essential locations as a map view, and users can filter the places such as hospitals, food delivery places, and temporary accommodation locations. When selected, it is navigated using the google maps navigation system.
    \item The system provides users the valid active hospitals, evacuation points, safe gathering places, and temporary accommodation places in the disaster area to download as a pdf format. Moreover, in the file for all locations, they validate whether the information is correct and google maps navigation links.
    \item The system provides users to select the city where they live so that it filters the information accordingly.
    \item The system provides users with valid solidarity campaigns, monetary donation links, and blood and stems cell donation places. 
\end{itemize}

\section{Stakeholders and their concerns}

There are three main stakeholders of the system: the volunteers, victims, developers. \\

Volunteers are the ones who are trying to help the victims by sharing information with website. Their concern is to reach and help most victims possible.\\

Victims are the ones who affected from the earthquakes, physically, mentally, or financially. Their concern is to get the help they need, such as food, healthcare, etc.\\

Developers are the ones build and maintain the website. Their concern is to build a bridge between victims and volunteers. They try to achieve this by verifying and entering information given by volunteers to website as fast as possible, and maintaining and securing the website to make it reachable by victims.\\

